---
title: "02_add_new_places"
author: "Harshvardhan"
format: html
editor: visual
---

## Purpose

This notebook is used for adding new places to the map. Every once in a while --- or if we get Threads like popularity then every day --- we would add new places to the Map. This notebook has functions that:

1.  read in the Google sheet and then creates a tibble of the places
2.  Reads in the existing the master,
3.  Finds which places do not have Google data yet,
4.  Use Google Places API to get information for those places
5.  Update master data with new data

## Import Libraries etc.

First step is to load the packages.

```{r}
setwd("/Users/harshvardhan/Documents/Useful-Files/Misc/Map of Tiny Perfect Things/map-of-tiny-perfect-things/")
```

```{r}
# install and load necessary packages
# install.packages(c("googledrive", "googlesheets4"))
library(googledrive)
library(googlesheets4)
library(tidyverse)
library(googleway)
```

Authenticating with Google Sheets:

```{r}
# set your googledrive token
# Note: You'll have to authenticate your session the first time you use this
# Simply run the following function and follow the instructions
# drive_auth()
```

Getting API right:

```{r}
# API key function
read_api_key = function(file_path) {
   # returning the first line of the text file at the file_path
   return(readLines(file_path)[1])
}
```

```{r}
# API Key (Harsh's API Key)
api_key = read_api_key("google_places_api_key.txt")

# load googleway
library(googleway)
set_key(key = api_key)
```

## Getting the sheet

```{r}
# define the URL of your Google Sheet
url = "https://docs.google.com/spreadsheets/d/1UC2EvXsafSjDkNNZSnC8eB_FPwyy1KenFfhUveoKEoc/edit#gid=1196848595"
```

```{r}
# get the ID of the Google Sheet from the URL
# capturing the sheet id to use with drive_get()
sheet_id = sub(".*/d/(.*)/.*", "\\1", url)

# get info about the Google Sheet
sheet_info = drive_get(id = sheet_id)

sheet_info
```

## Reading each sheet

Define the sheets to read

```{r}
sheet_names = c("Dea - Bay Area", "Dea - NYC + DC + NJ", "Dea - PNW", "Dea - Vegas", "Harsh - Knoxville", "Harsh - PNW", "Meenal - Bangalore") 
```

## Function to read in the Google sheet and create a tibble of the places

```{r}
read_google_sheet = function(url,
                             sheet_name,
                             cols_to_keep = c("name", "type", "location",
                                              "creators_rec", "notes")) {
   df = read_sheet(url, range = sheet_name) %>%
      janitor::clean_names() %>%
      select(all_of(cols_to_keep)) %>%
      mutate(sheet_name = sheet_name)
   
   return(df)
}
```

```{r}
# Apply the function to each sheet and combine into a single data frame
data_in_sheets = purrr::map_dfr(sheet_names, ~ read_google_sheet(url, .))
```

## Function to read in the existing master data CSV file provided a path

```{r}
read_master_data = function(file_path) {
   df = read_csv(file_path, stringsAsFactors = FALSE) %>%
      as_tibble()
   return(df)
}
```

```{r}
master_data = read_csv("master_data.csv")
master_data
```

## Data which is in sheets but not in master data should be added to master data

## Which places do not have Google data yet?

I would check for all columns.

```{r}
missing_data = master_data %>%
   filter(
      is.na(address) |
         is.na(rating) |
         is.na(user_ratings_total) |
         is.na(google_maps_link) | is.na(lat) | is.na(lng)
   )

missing_data
```

## Function to get information from Google Maps, given place name and area.

```{r}
get_city_state_country = function(address) {
    # Use google_geocode() to get information about the address
    geocode_result <- google_geocode(address)

    # The city name is usually contained in the 'locality' field
    city = purrr::map_chr(geocode_result$results$address_components, function(x) {
        if ("locality" %in% x$types) {
            return(x$long_name)
        } else {
            return(NA)
        }
    })

    # The state is usually contained in the 'administrative_area_level_1' field
    state = purrr::map_chr(geocode_result$results$address_components, function(x) {
        if ("administrative_area_level_1" %in% x$types) {
            return(x$long_name)
        } else {
            return(NA)
        }
    })
    
    # The country is usually contained in the 'country' field
    country = purrr::map_chr(geocode_result$results$address_components, function(x) {
        if ("country" %in% x$types) {
            return(x$long_name)
        } else {
            return(NA)
        }
    })

    return(list(city = city, state = state, country = country))
}
```

```{r}
get_place_info = function(place_name, area) {
  if (is.na(area)){
    print(paste0("Area name not provided for place ", place_name))
    return(
      tibble(
        name = place_name,
        address = NA,
        city = NA,
        state = NA,
        country = NA,
        rating = NA,
        user_ratings_total = NA,
        google_maps_link = NA,
        lat = NA,
        lng = NA
      ))
  }

  # Construct the search query
  query = paste0(place_name, " ", area)

  # Perform a Google Places search
  result_search = google_places(search_string = query)

  if (length(result_search$results) == 0) {
    print(paste0("Couldn't find place ", place_name, " in ", area))
    
    return(
      tibble(
        name = place_name,
        address = NA,
        city = NA,
        state = NA,
        country = NA,
        rating = NA,
        user_ratings_total = NA,
        google_maps_link = NA,
        lat = NA,
        lng = NA
      )
    )
  } else {
    # Extract the information
    print(paste0("Working on ", place_name, " ", area))
    result_details = result_search$results[1,]
    place_id = result_details$place_id
    address = result_details$formatted_address

    # Get city, state, country
    location = get_city_state_country(address)
    city = location$city
    state = location$state
    country = location$country

    rating = result_details$rating
    user_ratings_total = result_details$user_ratings_total
    google_maps_link = paste0("https://www.google.com/maps/search/?api=1&query=", URLencode(address), "&query_place_id=", place_id)
    lat = result_details$geometry$location$lat
    lng = result_details$geometry$location$lng

    return(
      tibble(
        name = place_name,
        address = address,
        city = city,
        state = state,
        country = country,
        rating = rating,
        user_ratings_total = user_ratings_total,
        google_maps_link = google_maps_link,
        lat = lat,
        lng = lng
      )
    )
  }
}

```

## Use Google Places API to get information for those place

```{r}
new_info = missing_data %>% 
   split(1:nrow(.)) %>% 
   map_dfr(~ get_place_info(.$name, .$location)) # purrrr, says Hadley's cat
```

## Update master data with new data

```{r}
add_new_rows = function(df1, df2, cols_to_match = c("name")) {
  # Use anti_join to find rows in df2 that are not in df1
  new_rows = df2 %>%
    dplyr::anti_join(df1, by = cols_to_match)
  
  # Add these new rows to df1
  df1 = rbind(df1, new_rows)
  
  return(df1)
}
```

```{r}
master_data = master_data %>% 
   add_new_rows(new_info)
```

## Investigations for repeated names.

Checking if any names are repeated. It is critical to have unique names of the places.

```{r}
# Find names that are repeated
master_data %>%
  group_by(name) %>%
  summarise(count = n()) %>%
  filter(count > 1)
```

## Adding ID

I think its unreasonable to assume that names of places will be unique forever. Languages are full of "false friends" --- words in two languages that look or sound similar but have different meanings.

Unrelated but some examples:

1.  The word "gift" in English means a present or something given, while in German, "Gift" means poison.

2.  The word "kiss" in English refers to an act of affection, while in Swedish, "kiss" means pee or urine.

3.  The word "blessed" in English generally means being favored, fortunate, or holy. However, in Portuguese, "blessed" translates to "abençoado."

4.  The word "molesto" in Spanish translates to "annoying" or "bothersome," but in Italian, "molesto" means "ill" or "unwell."

5.  The word "rude" in English typically means impolite or offensive. However, in French, "rude" translates to "rough" or "tough."

Anyway, this function will ID.

```{r}
add_unique_id = function(df) {
   # Check if unique_id column already exists
   if (!"unique_id" %in% names(df)) {
      # If not, create it
      df = df %>%
         # Arrange by location to ensure consistency
         arrange(location) %>%
         # Create an abbreviation for the location and remove special characters
         mutate(location_abbr = gsub("[^[:alnum:]]", "", 
                                     abbreviate(location, minlength = 4))) %>%
         # Create a group index
         group_by(location_abbr) %>%
         mutate(id_num = row_number()) %>%
         # Combine abbreviation and index into unique_id
         mutate(unique_id = paste(location_abbr, 
                                  sprintf("%04d", id_num), sep = "_")) %>%
         # Remove temporary columns
         select(-location_abbr,-id_num)
   }
   return(df)
}
```

```{r}
# Call the function
master_data_updated = add_unique_id(master_data) %>%
   # bringing unique id to front
   select(unique_id, name, location, everything())
master_data_updated
```

## Re-write Master Data with New Information

```{r}
master_data_updated %>%
   write_csv(file = "master_data.csv",
             na = "")
```

## Which cities are most represented?

```{r}
# Create a sorted bar plot for 'location'
master_data_updated %>%
  count(location) %>%
  ggplot(aes(reorder(location, n), n, fill = location)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = n), hjust = 1.4) +
  coord_flip() +
  theme_minimal() + 
  labs(x = "Location", 
       y = "Count", 
       title = "Number of Places by Location", 
       fill = "Location") +
   guides(fill = FALSE)
```

## What kind of places are most represented?

```{r}
# Create a sorted bar plot for 'type'
master_data_updated %>%
  count(type) %>%
  ggplot(aes(reorder(type, n), n, fill = type)) +
  geom_bar(stat = "identity") +
  #geom_text(aes(label = n), hjust = -0.3) +
  coord_flip() +
  theme_minimal() +
  guides(fill = FALSE) +
  labs(x = "Type", 
       y = "Count", 
       title = "Number of Places by Type")
```

## In summary...

```{r}
master_data_updated %>%
   ggplot(aes(x = type)) +
   geom_bar(aes(fill = type)) +
   facet_wrap( ~ location, scales = "free_y") +
   labs(x = "Type",
        y = "Count",
        title = "Distribution of Place Types in Each Location (Non-Uniform Y-Axis Scales)",
        fill = "Type") +
   theme_bw() +
   theme(axis.text.x = element_text(
      angle = 90,
      vjust = 0.5,
      hjust = 1
   ),
   legend.position = "none")
```
