---
title: "02_add_new_places"
author: "Harshvardhan"
format: html
editor: visual
---

## Purpose

This notebook is the manual fallback path for ingestion.

Default ingestion is automated by:

- `data_creation/auto_ingest_submissions.py`
- `.github/workflows/auto-sync-submissions.yml`

The notebook remains available for one-off manual runs and debugging.

## Submission Source (Netlify Forms)

Manual export (only if you are not using the automated script/workflow):

```bash
python data_creation/export_netlify_submissions.py --site-id "$NETLIFY_SITE_ID"
```

This creates `data_creation/place_submissions.csv`.

## Loading Packages

```{r}
library(tidyverse)
library(janitor)
library(googleway)
```

## Read Submissions + Master Data

```{r}
new_data = read_csv("data_creation/place_submissions.csv") %>%
  clean_names() %>%
  mutate(
    creators_rec = if_else(creators_rec_requested == "Yes", "Yes", NA_character_)
  )

master_data = read_csv("master_data/master_data.csv")
```

## Remove Duplicates

```{r}
remove_duplicates = function(new_df, old_df) {
  anti_join(
    new_df,
    old_df,
    by = c("name", "location", "city", "state", "country")
  )
}

non_duplicate_data = remove_duplicates(new_data, master_data)
```

## Google Places API Setup

```{r}
read_api_key = function(file_path) {
  readLines(file_path)[1]
}

api_key = read_api_key("google_places_api_key.txt")
set_key(key = api_key)
```

## Enrich Submissions with Place Details

```{r}
get_place_info = function(data) {
  name = data$name
  location = data$location
  city = data$city
  state = data$state
  country = data$country

  query = paste(name, location, city, state, country, sep = " ")
  result_search = google_places(search_string = query)

  if (length(result_search$results) == 0) {
    return(
      tibble(
        name = name,
        address = NA,
        rating = NA,
        user_ratings_total = NA,
        google_maps_link = data$google_maps_link,
        lat = NA,
        lng = NA,
        opening_hours = NA,
        type = NA,
        google_place_id = NA
      )
    )
  }

  result_details = result_search$results[1,]
  place_id = result_details$place_id
  address = result_details$formatted_address

  result_details_2 = google_place_details(place_id = place_id)
  opening_hours = if (!is.null(result_details_2$result$current_opening_hours$weekday_text)) {
    result_details_2$result$current_opening_hours$weekday_text %>% glue::glue_collapse(sep = "\n")
  } else {
    NA
  }

  tibble(
    name = name,
    address = address,
    rating = result_details$rating,
    user_ratings_total = result_details$user_ratings_total,
    google_maps_link = ifelse(is.na(data$google_maps_link), paste0(
      "https://www.google.com/maps/search/?api=1&query=",
      URLencode(address),
      "&query_place_id=",
      place_id
    ), data$google_maps_link),
    lat = result_details$geometry$location$lat,
    lng = result_details$geometry$location$lng,
    opening_hours = opening_hours,
    type = result_search$results$types[[1]][1],
    google_place_id = place_id
  )
}
```

```{r}
if (nrow(non_duplicate_data) > 0) {
  for (i in 1:nrow(non_duplicate_data)) {
    place = list(
      name = non_duplicate_data$name[i],
      location = non_duplicate_data$location[i],
      city = non_duplicate_data$city[i],
      state = non_duplicate_data$state[i],
      country = non_duplicate_data$country[i],
      google_maps_link = non_duplicate_data$google_maps_link[i]
    )

    new_info = get_place_info(place)

    if (i == 1) new_df_maps = new_info else new_df_maps = rbind(new_df_maps, new_info)
  }
} else {
  new_df_maps = tibble()
}
```

## Merge + Save

```{r}
if (nrow(non_duplicate_data) > 0) {
  new_places = left_join(non_duplicate_data, new_df_maps, by = "name") %>%
    select(
      name,
      location,
      city,
      state,
      country,
      creators_rec,
      notes,
      address,
      rating,
      user_ratings_total,
      google_maps_link,
      lat,
      lng,
      opening_hours,
      type,
      google_place_id,
      type2
    )

  df_all = bind_rows(master_data, new_places)
} else {
  df_all = master_data
}

write.csv(df_all, file = "master_data/master_data.csv", row.names = FALSE)
jsonlite::write_json(df_all, path = "master_data/master_data.json")
```
