---
title: "04_consolidate_categories"
author: "Harshvardhan"
format: html
editor: visual
---

## Purpose

<<<<<<< HEAD
This notebook reads `master_data.csv` and consolidates Google Maps provided category into three types: "coffee", "food", and "others".
=======
This notebook adds a column for type of place, consolidated to three categories: food, coffee, and others.

## Read Master Data
>>>>>>> 6389285c (edits)

```{r}
library(tidyverse)
```

<<<<<<< HEAD

## Function to use for consolidation
=======
```{r}
save_to_files = function(df) {
  # check if directory exists, if not create it
  if (!dir.exists("/master_data")) {
    dir.create("/master_data")
  }
  
  # write to csv and json files
  write.csv(df, file = "master_data/master_data.csv", row.names = FALSE)
  jsonlite::write_json(df, path = "master_data/master_data.json")
}
```

```{r}
df_all = read_csv("./master_data/master_data.csv")
```

Currently types in the data:
```{r}
df_all %>%
   group_by(type) %>% 
   count() %>% 
   arrange(desc(n))
```

Function to create type2:
>>>>>>> 6389285c (edits)

```{r}
consolidate_types = function(df) {
  # Create a new column "type2" based on the "type" column
  df_new = df %>%
    mutate(type2 = case_when(
      type %in% c("cafe") ~ "coffee",
      type %in% c("restaurant", "bakery", "bar", "meal_takeaway", "liquor_store", "meal_delivery") ~ "food",
      TRUE ~ "others"
    ))
  return(df_new)
}
```

<<<<<<< HEAD
## Read in Master Data

```{r}
df = read_csv("master_data/master_data.csv")
df
```

## Add type2

```{r}
df = consolidate_types(df)
```

## Save new data

```{r}
save_to_files = function(df) {
  # check if directory exists, if not create it
  if (!dir.exists("/master_data")) {
    dir.create("/master_data")
  }
  
  # write to csv and json files
  write.csv(df, file = "master_data/master_data.csv", row.names = FALSE)
  jsonlite::write_json(df, path = "master_data/master_data.json")
}


save_to_files(df)
```








=======
```{r}
df_all = consolidate_types(df_all)
```

Save data frame:

```{r}
save_to_files(df_all)
```

>>>>>>> 6389285c (edits)
